---
title: "__BUSN 32100 HW6__"
author: "Mia Jiang"
date: "11/15/2022"
output:
  pdf_document: default
urlcolor: blue
---

## 1. Setting WD and Loading Libraries
```{r, message = FALSE, warning = FALSE}
### Clear Global Environment
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.height = 4,
  fig.width = 6
)
rm(list = ls())
options(scipen = 0)
# Setting the Working Directory
setwd("~/Desktop/Fall Quarter/BUSN-32100/Week8/BUSN-32100-HW-6")
# Load packages
library(readr) # read csv
library(dplyr) # data manipulation
library(tidyverse) 
library(caret) # print text
library(reshape2) # melt data for correlation map plotting
library(ggplot2) # plotting
library(GGally) # pair plot
library(plotly) # interactive plot
```

## 2. Import data
```{r}
# Load data
kc_housing <- read_csv("kc_house_data.csv", show_col_types = FALSE)
```

## 3. Summary Statistics
```{r}
as.data.frame(summary(kc_housing)) %>%
  select(-Var1) %>%
  separate(Freq, into = c("attribute", "value"), sep = ":", extra = "merge") %>%
  mutate(attribute = str_remove(attribute, "\\.")) %>%
  pivot_wider(names_from = Var2,
              values_from = value)
```
## 4. Information on All Columns
```{r}
# Column info
glimpse(kc_housing)
# Missing values
summary(colSums(is.na(kc_housing)))
```

__*Answer*__  

- There are 21513 observations with 21 variables in total. For all columns, no missing value has been found in this data set.

## 5. Rename a column
```{r}
# Rename columns
kc_housing <- kc_housing %>%
  rename("sold_price" = "price", "constr_quality" = "grade")
# Check column names
names(kc_housing)
```
__*Note*__  

- Renaming the *price* column to make it more clear that the price refers to *sold price*. 

- Renaming the *grade* column to *constr_quality* so that it's more clear this column records __construction quality grade__ of houses.

## 6. Count number of houses by bedroom
```{r}
count(kc_housing, bedrooms) %>%
  arrange(desc(n))
```

__*Answer*__  

- 3-bedroom is the most popular type, as nearly half of the houses in this dataset have 3 bedrooms, followed by 4-bedroom and 2-bedroom types. In general, 3 or 4 bedrooms are the most common ones in Seattle, and it's relatively rare that a house has 5+ or less than 2 bedrooms.

## 7. Bar Chart of the Number of Bedrooms in Seattle Homes
```{r}
# Set color and theme
seattle <- "#00839A"
theme <- theme_bw() +
  theme(
    plot.title = element_text(size = 11, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face = "italic", hjust = 0.5),
    axis.title = element_text(size = 10, face = "bold")
  )
# Plot
ggplot(kc_housing) +
  geom_bar(aes(
    x = fct_reorder(as.factor(bedrooms), desc(bedrooms))
  ),
  stat = "count",
  fill = seattle
  ) +
  labs(
    title = "Distribution of Bedroom Quantity of Houses in Seattle",
    subtitle = "Year: 2014-2015",
    x = "Number of Bedrooms",
    y = "Count"
  ) +
  coord_flip() +
  theme
```

## 8. Mean Number of Bedrooms
```{r}
cat("The mean number of bedrooms in seattle houses between 2014 to 2015 is",
      mean(kc_housing$bedrooms))
```

## 9. Subsetting and selecting rows
```{r}
# Filter on bedrooms less than 5
clean_kc_housing <- kc_housing %>%
  filter(bedrooms < 5)
# Check new data
cat(
  "After excluding houses with 5 or more bedrooms, there are",
  nrow(clean_kc_housing), "observations left, which means",
  str_c(format(nrow(clean_kc_housing) / nrow(kc_housing) * 100, digits = 2), "%"),
  "houses in Seattle have less than 5 bedrooms between Year 2014 and 2015.",
  "Houses with 5 or more bedrooms are not typical."
)
```

## 10. Filter on multiple criteria
```{r}
# Filter on bedrooms less than 3 and living footage greater than 500
clean_kc_housing_2 <- kc_housing %>%
  filter(bedrooms < 3 & sqft_living > 500)
# Check new data
nrow(clean_kc_housing_2)
# Filter on bedrooms greater than 3 or floors greater than 2
clean_kc_housing_3 <- kc_housing %>%
  filter(bedrooms > 3 | floors > 2)
# Check new data
nrow(clean_kc_housing_3)
```

## 11. Find null values for price_sold
```{r}
summary(is.na(kc_housing$sold_price))
summary(kc_housing$sold_price == "")
```

__*Answer*__  

- There is no null value for the sold price of houses in this data set.

## 12. Group by and Apply on a Column
```{r}
kc_housing %>%
  group_by(view) %>% # group by view score
  summarise(mean_price = mean(sold_price), # calculate mean sold price
            median_price = median(sold_price)) # calculate median sold price
```

__*Answer*__  

- Unsurprisingly, houses with better views were sold with higher mean and median prices, i.e.e they are more expensive.

## 13. Pairplot of Numeric Columns
```{r, fig.height = 6, fig.width = 9}
# Select informative numeric columns
kc_housing_num <- kc_housing %>%
  select(sold_price:sqft_lot, constr_quality, yr_built)
# Plot
my_facet <- function(data, mapping, ...) { 
  ggplot(data, mapping) + 
    geom_point(...,
               color = seattle, alpha = 0.3, size = 0.1)
}

# Plot
ggpairs(kc_housing_num,
  lower = list(continuous = my_facet),
  upper = list(continuous = my_facet),
  diag = list(continuous = wrap("barDiag", bins = 30, 
                                alpha = 0.5, fill = seattle))
  ) +
  theme_bw(base_size = 8) +
  theme(axis.text = element_text(size = 6))
```

## 14. Correlation Heatmap
```{r}
# Calculate correlation
corr_mat <- round(cor(kc_housing_num), 2)
# Reshape correlation data
melted_corr_mat <- melt(corr_mat)
# Plot
plt <- ggplot(melted_corr_mat) +
  geom_tile(aes(Var1, Var2, fill = value)) +
  scale_fill_distiller(
    name = "Value",
    palette = "RdPu",
    direction = 1,
    breaks = seq(0, 1, 0.2),
    limits = c(0,1)
  ) +
  labs(title = "Correlation of House Index in Seattle") +
  theme(
    plot.title = element_text(size = 11, face = "bold", hjust = 0.5),
    axis.title = element_blank(),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.key.width = unit(0.8, "cm"),
    panel.background = element_blank()
  )
plt
# ggplotly(plt)
```